PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-08-18 txt/manuscript_short.tex
add more descirption on pros/cons

Finally, we should mention cross-entropy
benchmarking~\cite{boixo2018characterizing}, which was utlilized in validation
of the Sycamore-53 QPU supremacy experiments~\cite{arute2019quantum}. In this
approach, the quality of an algorithm implemented on the QPU is measured by
calculating the cross entropy of bit-strings actually sampled from the QPU,
compared to ideal bitstrings.

@@

>>>>

@@

Compared to these approaches, our approach allows for very simple operational
interpretation of the scheme and its results. This is especially useful for
newcomers to the field, who may be put off by more complicated appraoches.
Another benefit is, epsecailly for advanced users, the ability to control
resources utilized during the benchmarking. We can consider here resources such
as entanglement or coherence. Finally, the figure of merit we wish calculate and
to which we compare are results is fairly simple to obtain. The main downside of
our approach is the exponential number of circuits we need to consider.
